\modLP{Identification of} Biological Regulatory Networks from Process Hitting models

### 2014-11-11 parts-asp.tex
typo

Answer Set Programming (ASP) is a logic programming paradigm \cite{Baral03, Baral10},
which has been chosen to address the enumeration of all admissible parametrizations.
%The motivations are following:
ASP can efficiently enumerate a large set of possible answers,
  and it is easy to constrain the answers according to some properties.
Applied to the models and constraints defined in this papers,
ASP appears to be efficient for tackling the inherent complexity of the enumeration of parametrizations.

>>>>

Answer Set Programming (ASP) is a logic programming paradigm \cite{Baral03, Baral10},
which has been chosen to address the enumeration of all admissible parametrizations.
%The motivations are following:
ASP can efficiently enumerate a large set of possible answers,
  and it is easy to constrain the answers according to some properties.
Applied to the models and constraints defined in this paper,
ASP appears to be efficient for tackling the inherent complexity of the enumeration of parametrizations.
